### 2012-11-15 ASA2013/asa2013.tex
la2pdf commit - 2012:11:15	17:45:53	(Thu15.Nov)

\begin{abstract}
The MVDR adaptive beamformer has lately been shown to improve image quality in active sonar systems, but at a major computational expense. This is because the estimation and inversion of a spatial covariance matrix is required for each image pixel. We target this problem by altering and mapping the MVDR algorithm to a GPU, and suggest three different solutions depending on the system size.

For systems with relatively few channels, we suggest arithmetic optimizations for the estimation step, and show how a GPU can be used to yield processing rates of more than 1\,Mpx/s. For larger systems  we show that frequency domain processing is preferable. This allows a comparable performance to be maintained at a negligible reduction in image quality. These GPU implementations consistently reduced the runtime by 2-3 orders of magnitude compared to our reference C and Matlab implementations.

>>>>

\begin{abstract}
The MVDR adaptive beamformer has been shown to improve image quality in active sonar systems, but at a major computational expense. This is because the estimation and inversion of a spatial covariance matrix is required for each image pixel. We target this problem by altering and mapping the MVDR algorithm to a GPU, and suggest three different solutions depending on the system size.

For systems with relatively few channels, we suggest arithmetic optimizations for the estimation step, and show how a GPU can be used to yield image creation rates of more than 1\,Mpx/s. For larger systems we show that frequency domain processing is preferable. This promotes high processing rates at a negligible reduction in image quality. These GPU implementations consistently reduced the runtime by 2-3 orders of magnitude compared to our reference C and Matlab implementations.
